M.Sc. Proposal: \\ \bigskip Computational Electrokinetics

### 2013-01-14 notes/thesis-latex-template/thesis.tex
Update thesis.

The computational grid is created to have fine resolution near the particle surface, while
approximating the far-away boundary conditions. The logarithmic discretization is motivated
by the solution of the linearized system at Section \ref{app:linear}, 
where the largest gradients in the solution are near the particle surface.
The discretization of boundary conditions far away from the particle may be improved
by including the linear correction from the asymptotic solution, or applying

For strong electric field ($\beta \gg 1)$, the nonlinear effects become dominant and
another boundary-layer structure is expected to form near the particle surface. 
In order to achieve high numerical accuracy, the grid discretization should be made finer
near the particle surface (at $r = 1$), while $R_{max}$ can be made smaller.
In addition, the continuation of the solution between different $\beta$ values
should advance in finer steps, for Newton method convergence.

>>>>

The computational grid is created to have fine resolution near the particle surface, while
approximating the far-away boundary conditions. The logarithmic discretization is motivated
by the solution of the linearized system at Section \ref{app:linear}, 
where the largest gradients in the solution are near the particle surface.
The discretization of boundary conditions far away from the particle may be improved
by including the linear correction from the asymptotic solution, or reformulation of
far-away boundary condition according to the asymptotic behavior of the analytic solution
far away from the particle.

For strong electric field ($\beta \gg 1)$, the nonlinear effects become dominant and
another boundary-layer structure is begins to form near the particle surface. 
In order to achieve high numerical accuracy, the grid discretization should be made finer
near the particle surface (at $r = 1$), while $R_{max}$ can be made smaller. Moreover, different discretization scheme may be used for
the $r$ coordinate, to have higher grid resolution near the particle.
In addition, the continuation of the solution between different $\beta$ values
should advance in finer steps, to ensure Newton method convergence.
